Curvature Enhance With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes

### 2013-01-08 documents/thesis/TQLBO-paper/Paper-Siggraph/paper.tex

%% LyX 2.0.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,annual]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

@@

% When you submit your paper for review, please use the \TOGonlineID''
% command to include the online ID value assigned to your paper by the
% submission management system. Replace '45678' with the value you were
% assigned.
\TOGonlineid{45678}

@@

% Paper title.
\title{Curvature Enhance with Laplacian Operator for Hybrid Quad/Triangle Meshes}

@@

% Author and Affiliation (multiple authors).
\author{paper 000X }
%\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}\\ Cimalab Research Group %
%\and Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}\\Cimalab Research Group}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

@@

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modeling polygonal mesh using
curvature enhancing. This method use our extension of Laplace Beltrami
operator for hybrid quad/triangle meshes to enhance global curvature
in the model. This work present a novel applications of curvature
enhancement in sculpting and modeling with subdivision surfaces and
weight vertex groups. We show a series of graphics examples that demonstrate
the quality, predictability and flexibility of our results.
\end{abstract}

@@

Over the last years have been developed novel techniques of modeling
that can generate a variety of shapes to look natural and realistic
\cite{Botsch2006}. Editing techniques have evolved from affine transformations
to advanced tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing and creation from sketches \cite{Igarashi1999,Gonen2012},
complex interpolation techniques \cite{Sorkine2004,Zhou2005}, among
others.

Traditional methods for smooth surfaces from coarse geometry like
Catmull-Clark have been widely developed \cite{Catmull1978,Stam1998},
these works generalize uniform B-cubic splines knot insertion to meshes,
some of them add control of the results with the use of creases to
produce sharp edges \cite{DeRose1998}, or the modification of weights
on the vertices that control locally the zone of influence \cite{Biermann2000},
instead our method performs a feature enhancement of the model allowing
parameterize the curvature of the surface creating a family of different
versions of the same object preserving detail and realistic natural
look of the original model.

Many types of brushes have been developed to sculpt meshes, brushes
that perform inflation lose detail when inflating the vertices \cite{Stanculescu2011},
our method allows inflation of the mesh vertices moving in the opposite
direction to the curvature preserving the shape and sharp features
of the model.

This work is organized as follows: In the section \ref{sub:1.1-Related-work}
show works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In the section \ref{sec:Laplacian-Smooth}
we describe the theoretical framework of the Laplacian operator for
polygon meshes; In the section \ref{sec:Proposed-Method} we present
our proposed method for curvature enhancement and applications on
subdivision surfaces and sculpting; Lastly some results are shown
in graphic examples of Laplacian operator for hybrid quad/triangle
meshes. Also shows some results of curvature enhancement applications
in sculpting, subdivision and modeling methods.

\textbf{Contributions} Our work present an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes representing a larger
spectrum of mesh that works with today eliminating the need for preprocessing
and allows the preservation of the original topology. With this operator
we proposed a method to generate family of parameterized shapes, in
a robust and predictable way. Our method enable to customization of
smoothness and curvature obtained during subdivision surfaces process.
We proposed a new brush for enhance silhouette features of mesh in
modeling and sculpting.

@@

Many tools have been developed for modeling based on Laplacian mesh
processing. Thanks to the kindness of the Laplacian operator these
tools have in common the need for preservation of the geometric details
of the surface for the different processes such as: free-form deformation,
fusion, morphing and other applications \cite{Sorkine2004}.

Methods for offset polygon meshes based on the curvature defined by
the Laplace Beltrami operator have been developed. These methods allow
adjusting shape offset by a constant distance with high enough precision
to minimize Hausdorf error. The problem with these methods is the
loss of detail caused by smoothing, which depends on the size of the
offset \cite{Zhuo2012}. In volumetric approaches on computing the
offset boundary that are based on distance field computation in point-based
representation, this methods the topology of the offset model can
be different from that the original geometry \cite{Chen2011}.

\cite{Gal2009} proposes automatic features detection and shape edition
with feature inter-relationship preservation. In analysis step they
define salient surface features how ridges and valleys with base on
first and second order curvature derivatives \cite{Ohtake2004}, and
angle-based threshold. In feature characterization step the curves
are classified by several properties as planar or non-planar, approximated
by line, circle or ellipse shapes, and so on. In edit step the user
define initial change over several feature and then this edit is propagated
over other features with base in your inter-relationships. This method
works fine with objects that have sharp edges composed of basic geometric
shapes such as lines, circles or ellipses but this method has difficulties
when models are smoother with organic forms and cannot find the features
to edit and preserve.

Digital sculpting is divided into two principal methods: based on
polygonal methods and voxel grids-based methods. Brushes for inflate
operations in polygonal methods only depends on the normal at each
vertex \cite{Stanculescu2011}, in grids-based some operations permit
add or remove voxels and then have that processing isosurfaces from
volume to produce polygonal meshes representation \cite{Galyean1991}.
The problem whit this type of operations is the difficult to maintain
surface details during larger scale deformation.

@@

The Laplacian Smooth techniques allows you to reduce noise on a mesh's
surface with minimal changes on its shape. Computer graphics objects
which have been reconstructed from real world, contain undesirable
noise. A Laplacian smoothing removes undesirable noise while still
preserves desirable geometry as well as the shape of the original
model.

The functional used in many Laplacian smoothing approach to constrain
energy minimization is based on a total curvature of a surface $S$.

@@

Consider a surface $S$ compound by a set of triangles around vertex
$v_{i}$. We can define the \textit{Voronoi region} of $v_{i}$ as
show in figure \ref{fig:voronoi_region}, The change in area produced
by move $v_{i}$ is named gradient of \textit{Voronoi region \cite{Pinkall1993,Desbrun1999,Meyer2003}.}

@@

The LBO has desirable features, one feature of the LBO is in direction
of surface area minimization, allowing us to minimize energy using
it on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).

@@

Our method allow the editing of geometric features using the curvature
enhancement and smoothing. Generating a parameterized family of shapes
using a set of vertices representing a coarse sketch of the desired
model. Our approach can be mixed with traditional or uniform subdivision
surfaces methods and is iterative and converges towards a continuous
and smooth version of the original model.

@@

Our method allows the use of soft constraints weighting the effect
of smoothing at each vertex based on a normalized weight, the weights
are assigned to the control vertices of the original mesh or. The
weights of the new vertices resulting from the subdivisions are calculated
by interpolation, allowing to modify the behavior of the method on
exact regions of the original model.

Our approach contain an extension of the Laplace Beltrami operator
for meshes composed by triangles and quads. Using meshes composed
by triangles and quads has been increasing in recent years due to
the flexibility of modeling tools as Blender 3D \cite{blender}. Today
many artists manually connecting vertices such that its edition allows
simplest way to perform animation processes and interpolation \cite{Mullen2007}.
For these reasons it is very important to develop an operator that
allows working with this type of mesh immediately, eliminating the
need to preprocessing the mesh to convert to triangles and losing
the original design made by users.

@@

All triangles and quads configurations of the 1-ring neighborhood
faces adjacent to $v_{i}$ can be simplified in five simple cases
how show in figure \ref{fig:LBO-basic-5-TQ}.

@@

Where $L$ is the $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
to $v_{i}$, $A_{i}$ is the ring area around $v_{i}$.

@@

The curvature enhancing use the change produced by Laplacian smoothing
in the inverse direction of the curvature flow for moves the vertices
in the portions of the mesh with most curvature. In this equation
we use a diffusion process:

@@

For solve the equation above we use implicit integration and a normalized
version of TQLBO matrix.

@@

The vertices $V^{t+1}$are enhance along their inverse curvature normal
directions by solving this simple linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, $\mbox{sign}\left(x\right)$ is the sign function, and $\lambda dt$
is the enhance factor that support negative and positive values, negative
for enhancing positive for smoothing.

At the borders of the meshes that are not closed, you can not calculate
the curvature, for that reason we use the scale-dependent operator
proposed by \cite{Desbrun1999}.

Our method was designed for use with weight vertex groups to specify
the degree of impact on the solution, the weights vary between $0$
and $1$ with a value of $0$ makes no changes and with values 1 applies
the total change. The weights modifying influence zones where the
Laplacian is applied as shown in the equation \ref{eq:Lineal_System_with_wp}.
The weights on each vertex will produce a different solution for that
reason are put before obtaining the solution of the linear system.
Families of shapes that are generated may change substantially with
the weights of specific control points.

The model volume increases as the lambda is most negative, this can
be countered by a simple method of preserving volume. In \cite{Desbrun1999}
present a simple method to resize the mesh but have a problem the
model suffer large displacements with $\lambda<-1.0$ or perform multiple
iterations. We propose the following solution: If we have $v_{i}^{t+1}$
is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration, we define
$\overline{v}$ as:

@@

$\overline{v}$ is the center of the mesh, $vol_{ini}$ is an initial
volume, and $vol_{t+1}$ is the volume at the iteration $t+1$, then
we have that scale factor for resize the volume is

@@

and the new vertices positions are:

@@

We design a new brush that allows enhancement of the curvatures of
a polygon mesh in real time. Our brush work well with the stroke method
named \textsl{Drag Dot}  which allows you to preview the change that
occurs in the model until you release the mouse button or tablet,
also enable moves the mouse over the model to fit exactly where you
want to perform the enhancement of the curvature.

Brushes that perform similar work as inflate can create distortions
in the mesh and can also produce self-intersections of the mesh, as
this brushes only moves the vertices along the normal and does not
take into account the global information. Whereas our method look
for the best way to make inflation while keeping the global curvature
for preserving the shape and sharp features of the model.

Our method simplifies the work required for the enhancement, which
would be to use some different brushes for inflating and some other
to soften and styling. With our enhanced brush can be performed in
one step.

For the real-time work brush is necessary that the matrix is constructed
with the vertices that are within the radius defined by the user involvement,
which dramatically reduces the size of the matrix to be processed,
the center of this sphere depends on the place where the user clicks
on the canvas and three-dimensional mesh place where the click is
projected.

Furthermore special handling is necessary with the vertices are at
the boundary of which have neighbors that are not within the radius
of impact, these vertices must be marked as boundary and not the curvature
calculated for them, but must be present in the matrix to allow the
vertices that have all their neighbors within the selection radius
to calculate correctly the curvature, this change allows the results
to be much smoother on the border. The Laplacian matrix for sculpt
mode as a matrix equation.

@@

Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the center of sphere
the radius $r$. Then the matrix should remove rows and columns of
vertices index that are not within the radius.

@@

The Catmull-Clark subdivision transformation is used to smooth a surface
as the limit of sequence of subdivision steps\cite{Stam1998}. This
method do a recursive subdivision transformation that refines the
model into a linear interpolation that is a approximate smooth surface.
The process of Catmull-Clark is govern by properties of B-spline curve
from multivariate spline theory\cite{Loop1987}. In many subdivision
surfaces methods Catmull-Clark, Loop so on, the smoothness of the
model is automatically guaranteed \cite{DeRose1998}.

Catmull-Clark subdivision surface method generates smooth and continuous
models from a coarse model and produce results quickly due to the
simplicity of implementation, but with these methods is not easy to
make changes to the global curvature of the model. If we use Catmull-Clark
subdivision surfaces and curvature enhancement for modeling from coarse
models with few vertices can generate families of shapes with just
change a parameter, which would allow an artist to choose the model
of a similar set of options that best meets your needs without having
to change each one of the control vertices.

Our method allows the use of vertex weight paint over the control
points. The weights can be applied to the coarse model, then to perform
subdivision weights are interpolated, producing weights with smooth
changes in the zones of influence, so the curvature that is obtained
is much softer at those areas. Using vertex group weight and subdivision
surfaces is shown in figure \ref{fig:Subdivision-Cups}.c.

In the equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
matrix with weights corresponding to each vertex. The weights at each
vertex produce a different solution for this reason the matrix is
placed in the diffusion equation, as families that are generated may
change substantially with weighted of specific control points.

@@

In this section we describe the results of our curvature enhance method
that used our extension of Laplace Beltrami operator for hybrid quad/triangle
meshes with several example models in figures \ref{fig:Spectrum},
\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}. We test the curvature
enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
GHz and 8 GB RAM.

Figure \ref{fig:TQLBO_test} show the results when applying Laplace
Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) Laplacian smoothing
was applied to the model consists of only quads. In column (d) the
model was converted to triangles and then Laplacian smoothing was
applied. In column (e) the model is converted randomly some quads
into triangles and then Laplacian smoothing was applied, showing similar
results to those composed only of triangles or squares.

@@

Figure \ref{fig:camello_enhanced} show the generation of different
version of camel with the variation of parameter lambda. In the top
row you can see results of do curvature enhance over all model, as
the lambda becomes more negative curvature in this model makes close
in the concave parts and inflates on the convex parts as shown in
figure \ref{fig:Spectrum}. We use negative values to enhance model
silhouette features, among more negative the lambda, the model will
be further enhanced the silhouette features. In the bottom row of
the figure \ref{fig:camello_enhanced} can be observed using weighted
vertex groups, which allows you to specify which areas you want to
model enhancement, on the left is the enhancement of the legs of the
camel produces enhancement of organic aspect, also notes that the
border is not distorted and smooth in the union.

@@

Our method for enhancement of the silhouette features is predictable
and invariant under isometric transformations as those present in
some animations (see Figure \ref{fig:Animated_Camell}) in this animation
shows some poses of a camel doing a walk. In this animation the legs
and neck are the parts that enhancement is performed as shown in the
bottom left part of the figure \ref{fig:Animated_Camell}. Local modifications
produced by methods such as pose interpolation or animation rigging
not significantly affect the result as with camel legs in each sample
pose different flexion of the leg joints enhancement camel keeps flesh-like
shapes in the pattern produced original by the artist. This is due
to the diffusion process which is subjected to the mesh so that small
local changes are treated without significantly affecting global solution.
Our method is invariant of rotation, since depends solely the normal
field of the mesh, wish is invariant under global rotations.

Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
brush for sculpting in real time. One pass was used with the brush
as shown in the figure with the blue and red radius. In the bottom
of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
and looks like two bubbles stuck, so do the fingers on the bottom
of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
we see better results because not lost the shape of the silhouette
and kept the details of the fingers and leg. Similar results can be
obtained by an artist but it would take several steps and the use
of several brushes with curvatures enhancement only takes one step.
With this new method can easily enhance organic features how muscles
during the sculpting process. In figure \ref{fig:Performance-sculpt}
we show the performance of curvature enhancement brush, in this experimet
we use three models with 12K, 40K and 164K vertices, this models were
sculpted with curvature enhance brush in eache step the brush sphere
contain a variable number of vertices for processing. The processing
time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
times are good, because usually an artist sculpts a model for parts,
and each part is represented by an average of about 3000 vertices
in the models we use.

>>>>

%% LyX 2.0.2 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,review]{acmsiggraph}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amssymb}
\usepackage{graphicx}

@@

% When you submit your paper for review, please use the \TOGonlineID''
% command to include the online ID value assigned to your paper by the
% submission management system. Replace '45678' with the value you were
% assigned.
\TOGonlineid{XXXXX}

@@

% Paper title.
\title{Curvature Enhance With and Adapted Laplacian Operator For Hybrid Quad/Triangle Meshes}

@@

% Author and Affiliation (multiple authors).
\author{Alexander Pinzon\thanks{e-mail: apinzonf@gmail.com}
\qquad  Eduardo Romero\thanks{e-mail:edromero@unal.edu.co}
 \\Cimalab Research Group\\National University of Colombia}
%\and Ton Roosendaal\thanks{e-mail:ton@blender.org}\\ Blender CEO}

@@

\maketitle
\maketitle 
\begin{abstract}
This paper proposes a novel method for modeling a polygonal mesh by
enhancing the object curvature. This method uses an adapted extension
of the Laplace Beltrami operator for hybrid quad/triangle meshes,
to enhance the global curvature. Along with the method, this work
also presents new applications of curvature enhancement in sculpting
and modeling with subdivision surfaces and weight vertex groups. A
series of graphics examples demonstrates the quality, predictability
and flexibility of the method in a real production environment with
software blender.
\end{abstract}

@@

Over the last years several modeling techniques have been developed
to generate a variety of shapes that look natural and realistic\cite{Botsch2006}.
Editing techniques have evolved from affine transformations to advanced
tools like sculpting \cite{Coquillart1990,Galyean1991,Stanculescu2011},
editing and creation from sketches \cite{Igarashi1999,Gonen2012},
and complex interpolation techniques \cite{Sorkine2004,Zhou2005}.

Traditional methods for smoothing surfaces from coarse geometry, like
the Catmull-Clark, have become widely popular \cite{Catmull1978,Stam1998}.
These works generalize the uniform B-cubic splines knot insertion
to meshes, some of them adding some type of control, for instance
with the use of creases to produce sharp edges \cite{DeRose1998},
or the modification of weights on the vertices to locally control
the zone of influence \cite{Biermann2000}. Instead, the presented
method performs a feature enhancement of the model by parameterizing
the surface curvature and thereby creating a family of different versions
of the same object, preserving therefore the detail of the original
model and a realistic appearance.

On the other hand, many types of brushes have been developed to sculpt
meshes. Brushes that perform inflation end up by losing detail when
inflating the vertices \cite{Stanculescu2011}, in contrast the presented
method allows inflation of the mesh vertices by moving them towards
the opposite curvature direction, conserving the shape and sharp features
of the model.

\textbf{Contributions} This work presents an extension of the Laplace
Beltrami operator for hybrid quad/triangle meshes representing a larger
mesh spectrum from what has been presented so far. The method eliminates
the need of preprocessing and allows preservation of the original
topology. Likewise, along with this operator, it is proposed a method
to generate a family of parameterized shapes, in a robust and predictable
way. This method enables customization of the smoothness and curvature,
obtained during the subdivision surfaces process. Finally, it is proposed
a new brush for enhancing silhouette mesh features in modeling and
sculpting.

This work is organized as follows: Section \ref{sub:1.1-Related-work}
presents works related to the Laplacian mesh processing, digital sculpting,
and offsetting methods for polygonal meshes; In section \ref{sec:Laplacian-Smooth}
, it is described the theoretical framework of the Laplacian operator
for polygon meshes; In section \ref{sec:Proposed-Method}, it is presented
the method for curvature enhancement and applications of subdivision
of surfaces and sculpting; finally some Laplacian operator results,
to hybrid quad/triangle meshes are graphically shown as well as results
of the curvature enhancement applications in sculpting, subdivision
and modeling.

@@

Many tools have been developed for modeling, based on Laplacian mesh
processing. Thanks to the advantages of the Laplacian operator, these
different tools preserve the surface geometric details when using
them for different processes such as free-form deformation, fusion,
morphing and other application\cite{Sorkine2004}.

Offset polygon mesh methods, based on the curvature defined by the
Laplace Beltrami operator, have been developed. These methods adjust
the shape offset by a constant distance, with high precision as to
minimize the Hausdorf error. Nevertheless, these methods fail to conserve
enough detail because of the smoothing, a crucial issue which depends
on the offset size\cite{Zhuo2012}. In volumetric approaches for point-based
representation the computing the offset boundary that are based on
distance field computation, when performing the offset, the topology
of the model may be different from the original, changing the original
design \cite{Chen2011}.

\cite{Gal2009} proposes automatic features detection and shape edition
with feature inter-relationship preservation. They define salient
surface features like ridges and valleys with based the first and
second order curvature derivatives \cite{Ohtake2004}, and angle-based
threshold. Later the curves are classified by several properties as
planar or non-planar, approximated by lines, circles, ellipses and
other complex shapes. In then the user defines an initial change over
several features and then this change is propagated over other features
with base in the classified shapes and the inter-relationships between
these. This method works fine with objects that have sharp edges composed
of basic geometric shapes such as lines, circles or ellipses but method
has problems to classify when models are smoother with organic forms
because it cannot find the features to edit and preserve.

Digital sculpting can be divided into two principal approaches: based
on polygonal methods and voxel grid-based methods. Brushes for inflate
operations in polygonal methods only depends on the normal at each
vertex \cite{Stanculescu2011}, in grid-based sculpting some operations
allow to add or remove voxels, for produce polygonal meshes require
processing isosurfaces from volume \cite{Galyean1991}. The problem
whit this type of operations is the difficult to maintain surface
details during larger scale deformation.

@@

Computer graphics objects which have been reconstructed from real
world, contain undesirable noise. Laplacian Smooth techniques allow
noise reduction on a mesh's surface with minimal changes on its shape
while still preserves desirable geometry as well as the shape of the
original model.

The functional used in many Laplacian smoothing approaches to constrain
energy minimization is based on a total curvature of a surface $S$.

@@

Consider a surface $S$ composed by a set of triangles around vertex
$v_{i}$. We can define the \textit{Voronoi region} of $v_{i}$ as
show in figure \ref{fig:voronoi_region}, The change in the area produced
by the movement of $v_{i}$ is named gradient of \textit{Voronoi region
\cite{Pinkall1993,Desbrun1999,Meyer2003}.}

@@

The LBO has desirable features: one feature of the LBO is in direction
of surface area minimization, allowing to minimize energy using it
on a total curvature of a surface $S$ at equation (\ref{eq:total_cuarvature_integral}).

@@

Our method allows the editing of geometric features using the curvature
enhancement and smoothing, generating a parameterized family of shapes
from a set of vertices which represent a coarse sketch of the desired
model. Our approach can be mixed with traditional or uniform subdivision
surfaces methods, is iterative and converges towards a continuous
and smooth version of the original model.

@@

Our method allows the use of soft constraints weighting the effect
of smoothing at each vertex based on a normalized weight, which are
assigned to the control vertices of the original mesh or. The weights
of the new vertices resulting from the subdivisions are calculated
by interpolation, allowing modifying the behavior of the method on
specific regions of the original model.

Our approach is based on an extension of the Laplace Beltrami operator
for meshes composed by triangles and quads. Interest on meshes composed
by triangles and quads has increasing in recent years due to the flexibility
of modeling tools as Blender 3D \cite{blender}. Today many artists
manually connect vertices such that its edition allows a simple way
to perform animation processes and interpolation \cite{Mullen2007}.
For these reasons it is very important to develop an operator that
allows working with this type of mesh immediately, eliminating the
need to preprocessing the mesh to convert to triangles and losing
the original design made by users.

@@

Thus triangles and quads configurations of the 1-ring neighborhood
faces adjacent to $v_{i}$ can be simplified to five cases shown in
figure \ref{fig:LBO-basic-5-TQ}.

@@

Where $L$ is a $n\times n$ matrix, $n$ is the number of vertices
of a given mesh $M$, $w_{ij}$ is the TQLBO defined in equation (\ref{eq:TQLBO_wij}),
$N\left(v_{i}\right)$ is the 1-ring neighborhood with shared face
to $v_{i}$, $A_{i}$ is the ring area around $v_{i}$.

@@

The curvature enhancing uses the inverse direction of the curvature
flow to move the vertices in the portions of the mesh with most curvature.
In this equation we use a diffusion process:

@@

To solve the equation above we use implicit integration and a normalized
version of TQLBO matrix.

@@

The vertices $V^{t+1}$are enhanced along their inverse curvature
normal directions by solving the linear system: $Ax=b$, where $A=I-\left|\lambda dt\right|W_{p}L$,
$L$ is the Normalized TQLBO defined in the equation (\ref{eq:TQLBO-Normalized_Matrix}),
$x=V^{\prime}$ are the smoothing vertices, $b=V^{t}$ are the actual
vertices positions, $W_{p}$ is a diagonal matrix with weight vertex
group, and $\lambda dt$ is the enhance factor that support negative
and positive values, negative for enhancing positive for smoothing.

The curvature cannot be calculted at the border of the meshes that
are not closed, for that reason we use the scale-dependent operator
proposed by \cite{Desbrun1999}.

Our method was designed for use with weighted vertex groups which
specify the final curvature enhancement on the solution, these weights
vary between $0$ and $1$ with a value of $0$ makes no changes and
with values 1 applies a maximal change. The weights modify influence
zones where the Laplacian is applied as shown in the equation \ref{eq:Lineal_System_with_wp}.
Families of shapes that are generated may change substantially with
the weights of specific control points.

The models volume increases as the lambda is larger and negative,
this can be go against by a simple method of volume preservation.
In \cite{Desbrun1999} presents a simple method to resize the mesh
however the model suffers large displacements when $\lambda<-1.0$
or after multiple iterations. We propose the following solution: If
$v_{i}^{t+1}$ is a mesh vertex of $V^{t+1}$ in the $t+1$ iteration,
we define $\overline{v}$ as:

@@

$\overline{v}$ is the center of the mesh, $vol_{ini}$ is an initial
volume, and $vol_{t+1}$ is the volume at the iteration $t+1$, then
we define a scale factor.

@@

The new vertices positions are:

@@

We designed a new brush that allows the enhancement of the curvatures
of a polygon mesh in real time. Our brush works well with the stroke
method named \textsl{Drag Dot}  which allows to preview the changes
in the model before you release the mouse button or pen tablet, also
allows to move the mouse over the model to fit exactly where you want
to perform the enhancement of the curvature.

Brushes that perform similar work as inflate can create distortions
in the mesh and can also produce self-intersections in the mesh, as
these brushes only move the vertices along the normal and do not take
into account the global information. Whereas our method looks for
the best way to make inflation while preserving the global curvature
retaining the several shape and sharp features of the model.

Our method simplifies the work required for the enhancement, which
would be to use some different brushes for inflating and some other
to soften and styling. With our enhanced brush in one step can be
performed.

For the real-time brush it necessary that the Laplacian matrix is
constructed with the vertices that are within the radius  of the sphere
defined by the user, which reduces the size of the matrix to be processed,
the center of this sphere depends on the place where the user clicks
on the canvas and three-dimensional mesh place where the click is
projected.

Furthermore special handling is required for the vertices at the boundary
which have neighbors that are not within the radius of the brush.
These vertices must be marked as boundary and the curvature will not
be calculated for them, but must be present in the matrix so that
every vertex has their neighbors within the selection, this change
allows the results to be much smoother on the border. The Laplacian
matrix for sculpt mode as a matrix equation.

@@

Where $v_{j}\in N\left(v_{i}\right)$, $u$ is the center of sphere
of radius $r$. The matrixes should remove rows and columns of vertices
index that are not within the radius.

@@

The Catmull-Clark subdivision transformation is used to smooth a surface
as the limit of a sequence of subdivision steps\cite{Stam1998}. This
process is governed by properties of B-splines curve from multivariate
spline theory\cite{Loop1987}. This method does a recursive subdivision
transformation that refines the model into a linear interpolation
that approximates a smooth surface. The smoothness of the model is
automatically guaranteed \cite{DeRose1998}.

Catmull-Clark subdivision surface methods generate smooth and continuous
models from a coarse model and produce results quickly due to the
simplicity of implementation, but with these methods is not easy to
make changes to the global curvature of the model. If we use Catmull-Clark
subdivision surfaces and curvature enhancement for modeling from coarse
models with few vertices can generate families of shapes changing
a single parameter, this would allow an artist to choose the model
from a similar set of options that best meets his/her needs without
having to change each one of the control vertices.

Our method allows the use of vertex weight paint over the control
points. The weights can be applied to a coarse model, then to perform
a Catmull-Clark subdivision where weights are interpolated, producing
weights with smooth changes in the zones of influence, so the obtained
curvature is much softer at those areas as shown in figure \ref{fig:Subdivision-Cups}.c.

In the equation \ref{eq:Lineal_System_with_wp}, $W_{p}$ is a diagonal
matrix with weights corresponding to each vertex. Weights at each
vertex produce a different solution for this reason the matrix is
placed in the diffusion equation, as families that are generated may
change substantially with weighted of specific control points.

@@

In this section we describe the results of our curvature enhance method
with the extension of the Laplace Beltrami operator for hybrid quad/triangle
meshes with several example models (see figures \ref{fig:Spectrum},
\ref{fig:Subdivision-Cups}, \ref{fig:Catmull_Clark}, \ref{fig:TQLBO_test},
\ref{fig:camello_enhanced}, \ref{fig:Sculpt_Brush}, \ref{fig:Performance-sculpt},
\ref{fig:(a)Monkey}, \ref{fig:Animated_Camell}). We test the curvature
enhance with TQLBO method on a PC with AMD Quad-Core Processor @ 2.40
GHz and 8 GB RAM.

Figure \ref{fig:TQLBO_test} show the results when applying Laplace
Beltrami Operator TQLBO of equation (\ref{eq:TQLBO_Simple_Matrix})
in a model with a simple subdivision. In column (c) Laplacian smoothing
was applied to the model consists of only quads. In column (d) the
model was converted to triangles and then Laplacian smoothing was
applied. In column (e) the model is converted randomly some quads
into triangles and then Laplacian smoothing is applied, showing similar
results to those composed only of triangles or squares.

@@

Figure \ref{fig:camello_enhanced} show the generation of different
versions of a camel according to parameter lambda. In the top row
you can see results of do curvature enhance over all model, as the
lambda becomes larger and negative in this model it inflates the convex
parts as shown in figure \ref{fig:Spectrum}. The larger $\lambda$
the larger enhancements on the model features. In the bottom row of
the figure \ref{fig:camello_enhanced} can be observed using weighted
vertex groups, which allows you to specify which areas you want to
model enhancement, on the left is the enhancement of the legs of the
camel produces enhancement of organic aspect, also notes that the
border is not distorted and smooth in the union.

@@

Our method for enhancement of the silhouette features is predictable
and invariant under isometric transformations as those present in
some animations (see Figure \ref{fig:Animated_Camell}) in this animation
shows some poses of a camel doing a walk. In this animation the legs
and neck are the parts that enhancement is performed as shown in the
bottom left part of the figure \ref{fig:Animated_Camell}. Local modifications
produced by methods such as pose interpolation or animation rigging
not significantly affect the result as with camel legs in each sample
pose different flexion of the leg joints enhancement camel keeps flesh-like
shapes in the pattern produced original by the artist. This is due
to the diffusion process which is subjected to the mesh so that small
local changes are treated without significantly affecting global solution.
Our method is invariant of rotation, this since depends solely the
normal field of the mesh, wish is invariant under global rotations.

Figure \ref{fig:Sculpt_Brush} shows the use of curvature enhancement
brush for sculpting in real time. One pass was used with the brush
as shown in the figure with the blue and red radius. In the bottom
of the figure \ref{fig:Sculpt_Brush}.b shows how the camel leg self-intersecting
and looks like two bubbles stuck, so do the fingers on the bottom
of figure. Using silhouette features enhancement in figure \ref{fig:Sculpt_Brush}.c
we see better results because not lost the shape of the silhouette
and kept the details of the fingers and leg. Similar results can be
obtained by an artist but it would take several steps and the use
of several brushes with curvatures enhancement only takes one step.
With this new method can easily enhance organic features how muscles
during the sculpting process. In figure \ref{fig:Performance-sculpt}
we show the performance of curvature enhancement brush, in this experiment
we use three models with 12K, 40K and 164K vertices, this models were
sculpted with curvature enhance brush in each step the brush sphere
contain a variable number of vertices for processing. The processing
time for 800 vertices in the camel paw (40k model) only take 0.1 seconds,
for 2600 vertices in leg and neck (model 40k) take 0.5 seconds, these
times are good, because usually an artist sculpts a model for parts,
and each part is represented by an average of about 3000 vertices
in the models we use.
